Manifold Destiny - or how to rig an election

### 2023-12-27 index.qmd
app_bal

```{webr-r}
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install(c("dplyr","purrr"))
library(ManifoldDestinyWASMP)
ls(package:ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
ls(package:ManifoldDestinyWASMD)
```

```{webr-r}
Countingprocess <- setRefClass("Countingprocess", 
			       fields=list(sdfc='data.frame',
					   rdfci='data.frame',
					   rdfc='data.frame',
					   rofc='data.frame',
                                           rdfce='data.frame', 
					   quintile='data.frame',
					   desms='data.frame', 
					   r2list='list', 
					   predet='list',
					   sumreg='vector', 
					   psel='vector', 
					   polyc='list',
					   radpar='vector',
					   parameters='list', 
					   preend='list', 
					   parampre='data.frame', 
                                           rotplotly='list',
					   se='list',
					   lx='list',
					   pl_2dsort='list',
					   pl_corrxy='list',
					   pl_rescro='list',
					   pl_3d_mani='list',  
					   all_pl_3d_mani='list',
					   enf='list',
					   mansysl='list',
					   gensysl='list',
					   exnrs='vector',
					   allvar='list',
					   eqpar='list',
					   loss_df='data.frame'
					   ))
Countingprocess$methods(initialize=function(sdfinp=NULL,
					   selvar=c('P','R','S','T','U','V'), 
					   polyn=9, 
					   sortby=alpha
					   ){

})
```

>>>>

```{webr-r}
webr::install("ManifoldDestinyWASMP", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install("ManifoldDestinyWASMD", repos = "https://lotariohw26.github.io/MD_WASMC")
webr::install(c("dplyr","purrr","magrittr","data.table"))
library(ManifoldDestinyWASMP)
ls(package:ManifoldDestinyWASMP)
library(ManifoldDestinyWASMD)
ls(package:ManifoldDestinyWASMD)
library(magrittr)
```

# Simulation
## R2 sim
```{webr-r}
dfm <- (function(x){data.frame(P=seq(1,x),RV=as.integer(rnorm(x,1000,30)))})(10)
probw <- c(m=0.51,s=0.10)
probva <- c(vdm=0.7,mdm=0.4,vds=0.10,mds=0.10)
probvb <- c(vdm=0.5,mdm=0.6,vds=0.10,mds=0.10)
ztech <- c(0,1)	
app_bal <- ballcastsim(dfm,probw,probva,probvb,ztech)
app_bal 
```

## Tower
```{webr-r}
P  <- c(1,2,3,4,5,6)
S  <- c(60,60,60,60,60,55)
T  <- c(40,40,40,40,40,40)
U  <- c(40,40,40,40,40,40)
V  <- c(60,60,60,40,40,40)
Up <- c(40,(40-5),(40-10),40,40,40)
Vp <- c(60,(60+5),(60+10),40,40,40)
R  <- c(200,200,200,200,200,200)

## Tower 1
ex1m <- as.matrix(cbind(S,T,U,V))
towi <- as.data.frame(ex1m) %>% 
  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
  dplyr::select(5:8) %>%
  t() %>%
  data.frame() %>%
  data.table::setnames(paste0("County_",1:6))

towi[3:4,1] <- ""
towi[4,2] <- ""

## Tower 2
ex2m <- as.matrix(cbind(S,T,Up,Vp))
towii <- as.data.frame(ex2m) %>% 
  dplyr::mutate(EDVst=paste0(.[,1],"/",.[,2])) %>%
  dplyr::mutate(MIVst_1=paste0(.[1,3],"/",.[1,4])) %>%
  dplyr::mutate(MIVst_2=paste0(.[2,3],"/",.[2,4])) %>%
  dplyr::mutate(MIVst_3=paste0(.[3,3],"/",.[3,4])) %>%
  dplyr::select(5:8) %>%
  t() %>%
  data.frame() %>%
  data.table::setnames(paste0("County_",1:6))
towii[3:4,1] <- ""
towii[4,2] <- ""

```

## Countinggraphs
```{webr-r}
pro_rec_ex1_e <- data.frame(P=c(1,2,3,4,5,6),S=S,T=T,U=U,V=V,R=R)
pro_rec_ex2_e <- data.frame(P=c(1,2,3,4,5,6),S=S,T=T,U=Up,V=Vp,R=R) 
pro_rec_ex1 <- pro_rec_ex1_e[1:3,]
pro_rec_ex2 <- pro_rec_ex2_e[1:3,]
pro_elc_ex1 <- Countinggraphs(pro_rec_ex1,polyn=1)
pro_elc_ex2 <- Countinggraphs(pro_rec_ex2,polyn=1)
#pr_rep_1 <- seloutput <- seloutput(selreport(pro_elc_ex1,md$app4))
#pr_rep_2 <- seloutput <- seloutput(selreport(pro_elc_ex2,md$app4))
cx <- round(pro_elc_ex1$sdfc$x,2)
cy <- round(pro_elc_ex1$sdfc$y,2)
czeta <- round(pro_elc_ex1$sdfc$zeta,2)
calpha <- round(pro_elc_ex1$sdfc$alpha,2)
clambda <- round(pro_elc_ex1$sdfc$lamda,2)
cg <- round(pro_elc_ex1$sdfc$g,2)
ch <- round(pro_elc_ex1$sdfc$y,2)
cGamma <- round(pro_elc_ex1$sdfc$Gamma,2)
```

# Applications
```{webr-r}

```
